%\documentclass[12pt]{article}
%\begin{document}

\hyphenation{FLEISCH-MANN}
%\hyphenation{}

{\Large \bf Acknowledgements} \\

First and foremost I would like to express my gratitude for having been able to be part of this fantastic research group and to work on such fascinating projects. Many thanks to my supervisor Prof. Dr. CHRISTIAN ENSS and Prof. LOREDANA GASTALDO for reviewing my thesis! \\ 

\noindent I am extremely grateful for the exceptional support I got from ANDREAS FLEISCHMANN, DANIEL HENGSTLER and LUKAS MÜNCH, which was a substantial contribution to the success of the projects. I also can't thank them enough for their large effort on reviewing and correcting my thesis during this process, these countless hours you invested made all the difference! \\ 

\noindent Additional credit goes to all the colleagues that supported me either through helpful discussions, assistance in the labs/cleanroom or by just being there to listen.  Particularly DAVID MAZIBRADA, ANNA FERRING-SIEBERT, FABIAN KRÄMER and ALEX STOLL need to be mentioned. Thanks to DANIEL UNGER for your endless effort to keep us caffeinated with delicious coffee. Thanks to my amazing office neighbors RUI YANG, DAVID MAZIBRADA, FABIAN KRÄMER, ALEX GERKEN, ANNA FERRING-SIEBERT, MARKUS RENGER and FELIX HENRICH that made me want to come back every day and feel at home. And to ARNULF BARTH for implementing the TCG evenings every 'thorsday' to round off the night after a long day of work. Everyone in this research group made the time here so enjoyable! You will all be greatly missed. \\

\noindent Last but not least, I want to thank everyone close to me. My amazing parents deserve all my gratitude for the unconditional and incredible support they gave me through all those years. Not a single page could've been written without you! I couldn't be happier to have you. \\ And, to my wonderful girlfriend ANA: Thank you so much for everything. You accompanied me through most years of my studies, where together we overcame all obstacles. I cannot imagine succeeding like this if it weren't for you. I am blessed to have you at my side!


%\end{document}